### 2023-02-26 calculus.tex
Begin describing mark insertion

The branches of if-else expressions may synthesize different types $\TMV_1$ and $\TMV_2$ as long as
they are consistent. The entire expression then synthesizes the join, or lowest upper bound,
$\TJoin{\TMV_1}{\TMV_2}$.

@@

>>>>

The branches of if-else expressions may synthesize different types $\TMV_1$ and $\TMV_2$ as long as
they are consistent. The entire expression then synthesizes the \emph{join}
$\TJoin{\TMV_1}{\TMV_2}$.

@@

The central component of the calculus is \emph{mark insertion}, a bidirectional system given by the
following mutually defined judgments. The synthetic insertion judgment
$\ctxSynFixedInto{\ctx}{\EMV}{\ECMV}{\TMV}$ establishes that under the context $\Gamma$, the
unmarked expression $\EMV$ is ``marked into'' the marked expression $\ECMV$, which synthesizes type
$\TMV$. Analogously, the analytic insertion judgment $\ctxAnaFixedInto{\ctx}{\EMV}{\ECMV}{\TMV}$
states that the unmarked expression $\EMV$ is marked into $\ECMV$, which analyses against type
$\TMV$.

% TODO need to better explain why it is bidirectional

\input{figs/calculus-mark-insertion}

The rules for mark insertion are given in \Cref{fig:calculus-mark-insertion}. Observe that they
mirror the typing rules for marked expressions closely: all possible outcomes for fallible premises
are handled and markings are inserted as needed. For example, ISVar and ISUnbound together handle
variable usages. The former yields the same variable in the marked language when it is bound. The
latter marks the variable as unbound if it is not found in the context.

We again find two rules governing the marking of function application. ISAp1 corresponds to MSAp1 as
the ``success case'', recursively marking $\EMV_1$ and $\EMV_2$. Accordingly, ISAp2 parallels MSAp2
as the ``error case''. Similarly, ISIf and ISInconsistentBranches correspond to MSIf and
MSInconsistentBranches, and IALam1, IALam2, and IALam3 correspond to MSLam1, MSLam2, and MSLam3.
